WASP-4 is accelerating towards the Earth

### 2020-01-16 paper/ms.tex
add rv_vs_activity_checks

Caveats: we of course checked the RV vs bisector scatter diagram, as
well as the RV vs other activity indicators, to ensure we weren't
seeing a spurious multi-hundred meter per second change.

>>>>

\subsection{Trend due to stellar activity?}

First, we considered whether the measured RV trend is correlated with
WASP-4's emission in the Ca II H \& K lines, as quantified with the
chromospheric $S$-index (CITE: Wright 2004).  We only analyzed the
HIRES velocities for this step, since they are the main source of
signal in our analysis.  First, we subtracted the orbital solution
from the Keck-HIRES velocities.  Then, following CITE Bryan 2016 and
2019, we calculated the Spearman rank correlation coefficient between
the $S$-index and the orbit-subtracted velocities.  We found a
correlation coefficient of 0.16, which weakly hints at a correlation,
but is not statistically significant (the corresponding $p$-value is
0.65).  We therefore do not think that the linear trend can be
attributed to stellar activity.
